---
title: "Case Study 2 -Stout"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r}
library(tidyr)
library(DT)
library(ggplot2)
library(dplyr)
library(tidyverse)
library(lubridate)
library(readxl)
library(lubridate)
library(scales)
library(RColorBrewer)
library(plotly)
library(readxl)
library(readr)
library(scales)
library(stringr)
library(boot)
library(reshape2)
```

```{r setup, include=FALSE}
setwd("~/Desktop/")
data <- read.csv("~/Desktop/casestudy.csv")
```

```{r}
df <- data.frame(data)
```

## Current revenue of 2017 is $31,417,495
```{r}
df %>%
 group_by(year) %>%
 summarise(Revenue =sum(net_revenue))
```

-   New Customer Revenue **e.g. new customers not present in previous year only**

    ```{r}
cust2017 <- df %>% 
     filter(year == 2017)

cust2016 <- df %>% 
     filter( year == 2016)

cust2015 <- df %>% 
     filter( year == 2015)


new_cust2017 <- anti_join(cust2017, cust2016, by = c("customer_email" = "customer_email"))
new_cust2016 <- anti_join(cust2016, cust2015, by = c("customer_email" = "customer_email"))

R2017<-new_cust2017 %>%
     summarise(Revenue_new_cust2017 = sum(net_revenue))
    ```
## Revenue for new customers 2017 is $28,776,235
```{r}
print(R2017)
```
## Revenue for new customers 2016 is $18,245,491
    ```{r}
R2016<- new_cust2016 %>%
summarise(Revenue_new_cust2016 = sum(net_revenue))
    ```
    
```{r}
print(R2016)
```
## Existing Customer Growth
```{r}
growth <- R2017-R2016
```

```{r}
print(growth)
```
## Total Customers form 2016 is 145,062.
```{r}
add_count(new_cust2016)
```
## Total customers from 2017 is 229,028.
```{r}
add_count(new_cust2017)
```

## Existing Customer Revenue Current 2017 is $2,641,260.
```{r}
totalrev2017<-sum(cust2017$net_revenue)
existingrev <- totalrev2017-R2017
print(existingrev)
```
## Existing Customer Revenue for 2016 is $7,485,453.
```{r}
totalrev2016 <- sum(cust2016$net_revenue)
existingrev2016<- totalrev2016-R2016
print(existingrev2016)
```
## New customers in 2017.
```{r}
head(new_cust2017,50)
```
## Loss of total revenue from 2016 to 2017 is $5,686,551.
```{r}
loss <- totalrev2017-totalrev2016
print(loss)
```
## Visuals
```{r}
hist(cust2016$net_revenue)
```
```{r}
hist(cust2015$net_revenue)
```

```{r}
hist(cust2017$net_revenue)
```

```{r}
 ggplot(df, aes(x=factor(year), weights=net_revenue)) + 
    geom_bar(col="red") + 
    theme_bw() + 
    labs(title="Revenue by Year", x="Year", y="$") + 
    theme(plot.title = element_text(hjust = 0.5))
```

Overall, looking at the data from 2015 to 2016 there was a slight decrease in net revenue but 
in 2017 it increased. When looking new customers year to year it seems from 2016 to 2017 there has 
been increase from 45,062 to 229,028. So far in 2017 net revenue has increased from year 2015 and 
2016 which is good sign. 